Lattice Boltzmann study of mass transfer for Bretherton/Taylor bubble train flow

### 2012-03-05 Text/introduction.tex
Small modifications.

\section{Introduction}
\label{intro}
The monolith reactors during last years are getting more attention as alternative to slurry
reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. The bubble flow we focus in
this work, so-called Bretherton-Taylor flow \cite{bretherton,taylor}, describes the flow through
a liquid medium of equal sized, long in comparison with the channel height bubbles, see
Fig. \ref{fig:benchmark:hydro}. This flow regime
is usually characterized by surface tension dominance over inertia and viscous effects and by
comparatively small gas flow velocities \cite{yue-mass}. Due to surface tension dominance and small
scales of microchannels, bubble train flow exhibit advantageous properties which can not be achieved
in macroscopic counterparts: such as thin films \cite{bretherton} can remarkably enhance mass
transfer in the film from a gas or from walls; the plug flow nature that separates liquid slugs from each
other allowing to perform chemical reactions in slugs \cite{kreutzer-overview} or be an indicator of
the liquid velocity \cite{taylor}; the flow pattern depending on the capillary number $Ca$
\cite{heil-bretherton,heil-threedim}.  Overall, nowadays one can find a large number of applications
of Bretherton-Taylor bubble train flow: continuous flow analyzers, lung openings, chemical reactions
as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. One can find a
lot of different application references in extensive reviews \cite{kreutzer-overview,
gupta-review,yue-mass}.

>>>>

\section{Introduction}
\label{intro}
The monolith reactors during last years are getting more attention as a promising alternative to slurry
reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. Monolith reactors usually operate in Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow through
a liquid medium of equally sized, long bubbles, see
Fig. \ref{fig:benchmark:hydro}. This flow regime
is characterized by surface tension dominance over inertia and viscous effects and by
comparatively small gas flow velocities \cite{yue-mass}. Due to surface tension dominance and small
scales of microchannels, bubble train flow exhibit advantageous properties which can not be achieved
in macroscopic counterparts: liquid thin films \cite{bretherton} between bubbles and walls remarkably enhance mass
transfer from gas and walls to liquid; the plug flow nature that separates liquid slugs from each
other allowing to perform chemical reactions in slugs \cite{kreutzer-overview} or be an indicator of
the liquid velocity \cite{taylor}; the flow pattern depending on the capillary number $Ca$
\cite{heil-bretherton,heil-threedim}.  Overall, nowadays one can find a large number of applications
of Bretherton-Taylor bubble train flow: continuous flow analyzers, lung openings, chemical reactions
as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. One can find a
lot of different application references in extensive reviews \cite{kreutzer-overview,
gupta-review,yue-mass}.
